Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
clean Disposition

stop_df <- read.csv("~/Desktop/Berkeley_PD_-_Stop_Data.csv")

#disps <- as.character(stop_df$Dispositions)
#max(nchar(disps))
#disps[which(nchar(disps) == 42)]

stop_df <- mutate(stop_df, Dispositions = as.character(stop_df$Dispositions))

#entries with "zz do not use Assist" 
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "zz do not use Assist", ""))
#entries with "FA - TIGHT"
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "FA - TIGHT", ""))
#fixing entries that were input incorrectly
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "[0]{6}[1]?", "00000"))

#deal with special cases first 
stop_df <- mutate(stop_df, Other = str_replace_all(stop_df$Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", ""))
stop_df <- mutate(stop_df, Other = str_replace_all(stop_df$Other, "^[ ,]{0,4}", ""))

stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))

>>>>

#read data
stop_df <- read.csv("~/Desktop/Berkeley_PD_-_Stop_Data.csv")

# Delete meaningless information and fix typos
stop_df <- stop_df %>%
  mutate(Dispositions = as.character(stop_df$Dispositions)) %>%
  mutate(Dispositions = str_replace(Dispositions, "zz do not use Assist", "")) %>%
  mutate(Dispositions = str_replace(Dispositions, "FA - TIGHT", "")) %>%
  mutate(Dispositions = str_replace(Dispositions, "[0]{6}[1]?", "00000"))

View(stop_df)
# Split people information and other information
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

OtherInformation <- c("P", "^M$", ", M$", "^M, P$")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, ))
stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))
